2-factor-Hull-White\_model\_calibration

### 2020-05-11 week7/Report.tex
Grammar
WIP

@@

In this paper we go beyond the constant risk-free continuously compounded rate.  There are several models to implement stochastic interest rates.  The short rate models which describe instantaneous continuously-compounded interest rate at time $t , r_t$ include the Vasicek model introduced in \cite{Vas1}, Mamon in \cite{Mamon1} advances this model by presenting approaches in obtaining the closed-form solution using the Vasicek model. Under the Vasicek model the short rate dynamics is given by,\\

@@

\section{LIBOR forward rates, stock paths, and counterparty firm values.
}

\section{Discount factor and Value of the Option
}

>>>>

    \usepackage{listings}

@@

In this paper, we go beyond the constant risk-free continuously-compounded rate.  There are several models to implement stochastic interest rates.  The short rate models which describe instantaneous continuously-compounded interest rate at time $t , r_t$ include the Vasicek model introduced in \cite{Vas1}, Mamon in \cite{Mamon1} advances this model by presenting approaches in obtaining the closed-form solution using the Vasicek model. Under the Vasicek model the short rate dynamics is given by,\\

@@

\section{LIBOR Forward Rates, Stock Paths, and Counterparty Firm Values
}
The zero coupon bond prices are provided as observed, which means that the interest rate can be determined in the calibration process, along with the other parameters needed for the model. The following code sets bounds for the parameters and finds optimal values within those bounds.
\begin{lstlisting}
#minimizing F
bnds = ((0,1),(0,0.2),(0,0.2), (0.00,0.10))
opt_val = scipy.optimize.fmin_slsqp(F, (0.3, 0.05, 0.03, 0.05), bounds=bnds)
opt_alpha = opt_val[0]
opt_b = opt_val[1]
opt_sigma = opt_val[2]
opt_r0 = opt_val[3]
\end{lstlisting}
Running this code results in the following values for the model parameters:
\begin{itemize}
    \item Optimal alpha: 0.273
    \item Optimal b: 0.069
    \item Optimal sigma 0.028
    \item Optimal r0: 0.075
\end{itemize}

\section{Discount Factor and Value of the Up-and-Out Call Option
}
Since this is a barrier option, it is necessary to use the 'mask' function to zero the payoffs that would exceed the barrier. This is done in the payoff function.
\begin{lstlisting}
# define payoff for up-and-out call option

def payoff(S_t, K, L):
    stopped_S = S_t.mask(S_t > L, 0)
    return np.maximum(stopped_S - K, 0).to_numpy()

# Estimate the default-free value of the option:

option_estimate = []
option_std = []

for month, path in share_prices.items():
    payoffs = payoff(path, K, L)
    option_price = np.exp(-risk_free*T)*payoffs
    option_estimate.append(option_price.mean())
    option_std.append(option_price.std()/np.sqrt(sample_size))
\end{lstlisting}
This calculates the mean value for the call option mean risk-free price as 1.200.
